---
title: "lee"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
```

```{r}
text <- readLines("~/scrapy/ralady/sources/galant_out2.txt")#read in text
empty <- grep("^$",text)
text <- text[-empty]
text <- stringr::str_replace(text,"                            ","")
text <- stringr::str_replace(text,"\f","")
outline <- grep("^ *[0-9]*\\.[0-9]",text)
text <- text[-outline]
fulllines <- grep("^[aA-zZ]",text)
text <- text[-fulllines]
spacy <- grep("^ [aA-zZ]",text)
text <- text[-spacy]
text <- str_trim(text)
text
```

nos <- grep("^[^0-9“”]",text)#remove lines that don't start with numbers
if(length(nos)>0){
  text <- text[-nos]
}
qs <- grep("^“",text)#Find lines that start with fancy quotes (i.e., translations that got cut)
for(i in 1:length(qs)){
  prev <- qs[i]-1
  text[prev] <- paste(text[prev],text[qs[i]])#reunite quotes with their example sentences
}
text <- text[-qs]
ls <- grep("“",text)
newtext<- vector(mode="character", length=length(ls))
for(i in 1:length(ls)){
  newtext[i] <- text[ls[i]]
}
cites <- grep("\\(.*[0-9][0-9][0-9][0-9].*\\)",newtext)#find cites (likely non-zapotec data points)
munro <- grep("\\(.*Munro",newtext)#remove those cited from other Zapotec scholars
nmcites <- setdiff(cites,munro)
newtext <- newtext[-nmcites]
secs <- grep("^[0-9]+\\.[0-9]+",newtext)#remove section headings with periods
newtext <- newtext[-secs]
secs2 <- grep("^[0-9]+ [aA-zZ]",newtext)#remove section headings without periods
newtext <- newtext[-secs2]
ungrammatical <- grep("\\*",newtext)#remove ungrammatical sentences
newtext <- newtext[-ungrammatical]
infelicitious <- grep("\\#",newtext)#remove infelicitious sentences
newtext <- newtext[-infelicitious]
splitt <- data.frame(Zap= character(0), Gloss=character(0), Trans=character(0),stringsAsFactors=FALSE)#create a dataframe
```